Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-08 docs/evol.tex
minor change in the threats to validity section

A threat to the internal validity of our experiment could be the false alarms of the
FindBugs tool. False positives and negatives of static analysis tools and
how they can be reduced is an issue that has already been discussed in literature (see
Section~\ref{sec:rel}). Furthermore, consider a false positive alarm where an
security bug is reported, but it is invalidated based on the context of the
application (an {\sc sql} injection vulnerability~\cite{RL12} in an application that
requires no external input).

>>>>

A threat to the internal validity of our experiment could be the false alarms of the
FindBugs tool. False positives and negatives of static analysis tools and
how they can be reduced is an issue that has already been discussed in literature (see
Section~\ref{sec:rel}). Furthermore, consider the case where a
security bug is reported, but it is invalidated based on the context of the
application. For instance, an {\sc sql} injection vulnerability~\cite{RL12}
in an application that requires no external input could be reported by FindBugs,
but in this case would be a false positive alarm.
